Dependent Object Types

### 2012-08-30 doc/candidacy/report.tex
spellcheck

Their calculus is grounded in type theory. It is based on Girard's
$F_\omega$~\cite{tapl}. They add {\it translucent sums} to model
modules, dependent functions to model functors, a notion of subtyping
to model module implementation-interface matching. The crucial
addition and novelty is that of a {\it translucent sum}. A translucent
sum has the form of a possibly empty sequence of bindings. Similarly,
a translucent sum type has the form of a possibly empty sequence of
declarations. They differ from traditional records, because they can
contain types and because later fields can depend on ealier
ones. Translucent sums are ordinary values. Since they model modules,
it means that modules are first-class values, and their module system
is higher-order ``for free''.

@@

Though Scala doesn't have virtual classes, its abstract types enable
it to emulate some (but not all) of the benefits of virtual classes as
presented in the Tribe calculus. On the other hand, Tribe doesn't have
virtual types. In a follow-up paper~\cite{tribalo}, an improved
variant of Tribe with simpler types, cross-family inheritance and
generics is presented and a formalisation of ownership types built
upon it.

@@

In~\cite{nuObj}, Odersky et al. presents ${\nu}Obj$, a calculus for
classes and objects which can have types as members. It proposes three
kinds of type members: aliases, abstract types, and new types. The
calculus can encode Java's inner classes, virtual types, family
polymorphism, essential aspects of the ML-like module systems
including sharing consraints and higher-order functors, and System
$F_{<:}$~\cite{tapl}. The calculus can be used as a basis for unifying
concepts that so far existed in parallel in advanced object systems
and module systems. ${\nu}Obj$ makes the following connections: Object =
Module, Object type = Signature, Class = Method = Functor.

@@

>>>>

Their calculus is grounded in type theory. It is based on Girard's
$F_\omega$~\cite{tapl}. They add {\it translucent sums} to model
modules, dependent functions to model functors, a notion of subtyping
to model module implementation-interface matching. The crucial
addition and novelty is that of a {\it translucent sum}. A translucent
sum has the form of a possibly empty sequence of bindings. Similarly,
a translucent sum type has the form of a possibly empty sequence of
declarations. They differ from traditional records, because they can
contain types and because later fields can depend on earlier
ones. Translucent sums are ordinary values. Since they model modules,
it means that modules are first-class values, and their module system
is higher-order ``for free''.

@@

Though Scala doesn't have virtual classes, its abstract types enable
it to emulate some (but not all) of the benefits of virtual classes as
presented in the Tribe calculus. On the other hand, Tribe doesn't have
virtual types. In a follow-up paper~\cite{tribalo}, an improved
variant of Tribe with simpler types, cross-family inheritance and
generics is presented and a formalization of ownership types built
upon it.

@@

In~\cite{nuObj}, Odersky et al. presents ${\nu}Obj$, a calculus for
classes and objects which can have types as members. It proposes three
kinds of type members: aliases, abstract types, and new types. The
calculus can encode Java's inner classes, virtual types, family
polymorphism, essential aspects of the ML-like module systems
including sharing constraints and higher-order functors, and System
$F_{<:}$~\cite{tapl}. The calculus can be used as a basis for unifying
concepts that so far existed in parallel in advanced object systems
and module systems. ${\nu}Obj$ makes the following connections: Object =
Module, Object type = Signature, Class = Method = Functor.

@@

Let's now illustrate with a few examples the correspondences outlined
earlier. %TODO
